\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-13 analytics/npa.tex
random
half of nps

\subsection{Trends}

@@

Figure \ref{fig:navs-combined} takes the navigations-per-add for every time a course was ever added by any Skedge user.

\subsection{Breaking them apart}

  behavioral patterns
  Direct search for specific course
  Discovery, browsing, exploring

  \subsubsection{Direct searches}

@@

    \caption{Etc}
    \label{fig:searchtypes}
  \end{figure}

  Why would 0-navs be so common with direct searches? 64\% of them subsections!

  \subsubsection{Browse}

@@

    \caption{Etc}
    \label{fig:searchtypes}
  \end{figure}

@@

>>>>

\subsection{General trends}

@@

Figure \ref{fig:navs-combined} shows the navigations-per-add breakdown for every time a section was added in Skedge. With 40\% of sections added in zero navigations and 39\% added within one navigation, it is immediately apparent that Skedge delivers users the content they look for in the vast majority of cases, assuming that the intention of the user was to add a course.

Considering the hypothesis claimed in Section 2.3.2 (that course selection criteria can be broken down to \emph{requirements}, \emph{electives}, and \emph{peer recommendations}), however, we ought examine if data for different use-cases are being conflated in this chart.

\subsection{Direct search (requirement criteria)}

@@

    \caption{Frequency of navigations-per-adds when the goal was to add a specific course}
    \label{fig:navs-direct}
  \end{figure}

  Direct searches are easy to distinguish, as we can take the subset of search queries that target a specific course, namely, those that \textbf{a)} contain both department and course code fields (e.g. ``{\tt csc 171}''), or \textbf{b)} contain a title field (``{\tt intro to programming}''). Figure \ref{fig:navs-direct} shows the navigations-per-add when, under this criteria, the user's goal was to add a specific course.

  The difference between these results and those in \ref{fig:navs-combined} is suble but logical. Users searching for a specific course should have an increased proportion of 1-navigation adds, as the graph shows, because the use-case is \emph{search for course}, \emph{add course}, perhaps occasionally taking an extra try to account for typos, not knowing the title or course code exactly, etc.

  But given this reasoning, why would 0-navigation adds still be so common in direct searches? Further analysis on only the sections that were added from direct search and with 0 navigations shows that 64\% of those sections are in fact \emph{subsections}. As happened in the illustrative example at the beginning of this section, this shows that a very common use-case is to add labs, workshops, etc. of a course directly after adding the main section.

  This hypothesis is further confirmed by doing the same analysis for ${navs}=1$ and ${navs}=2$, when the inverse behavior would be expected (it makes sense for subsections which were added seperately from their main sections to be more rate). Only 11\% of sections that were added from a direct search after 1 navigation are subsections, and that number drops to 8\% for 2 navigations.

\subsection{Browse (elective criteria)}

  Browsing behavior was done as a direct inverse of  harder to detect than direct search behavior, because there  query behavioral patterns
  Discovery, browsing, exploring

@@

    \caption{Frequency of navigations-per-adds/bookmarks when the goal was to browse for courses}
    \label{fig:searchtypes}
  \end{figure}

@@

\subsection{Peer-guided (recommendation criteria)}

  :(

### 2016-04-13 paper.tex
bib stuff
half of nps

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the three major use-cases associated with course scheduling---direct search, exploratory search, and peer recommendation---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

@@

\addcontentsline{toc}{chapter}{Bibliography}
\singlespacing

>>>>

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the two major use-cases associated with course scheduling---direct and exploratory search---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

@@

\singlespacing
